---
title: "ImmGen-scATAC Correlation"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r libraries, echo = FALSE, warning = FALSE, message = FALSE}
library(plotly)
library(heatmaply)
library(SummarizedExperiment)
```

# About
Using the kmer deviation score computation through chromVAR, I computed the scores for 512 k=5 mers 
and scored each of the ImmGen ATAC samples in addition to each of the single cells. 

There are two merged bam files that Marcin pointed me to on the Broad server, which are shown here. 
There may be additional samples on the Stanford server that I can add if this isn't sufficient. 

## ImmGen/ImmGen

```{r immgen, fig.width=7, fig.height=7, message = FALSE, warning = FALSE, echo=FALSE, cache = TRUE}
immgen <- assays(readRDS("../output/immgenDeviations.rds"),"z")[[1]]
corout <- cor(immgen, immgen, use = "pairwise.complete.obs")
heatmaply(t(corout), scale_fill_gradient_fun = ggplot2::scale_fill_gradient2(low = "blue", high = "red"))
```

## 0 Hour Samples
**Note: only 77,611 of the 512,595 peaks in ImmGen were non-zero for these 413 samples**

```{r zh, fig.width=7, fig.height=7, message = FALSE, warning = FALSE, echo=FALSE, cache = TRUE}
immgen <- assays(readRDS("../output/immgenDeviations.rds"),"z")[[1]]
zh <- assays(readRDS("../output/0hr_LPS_Deviations.rds"),"z")[[1]]
zh <- zh[,colSums(is.na(zh)) < 10]
corout <- cor(zh, immgen, use = "pairwise.complete.obs")
heatmaply(t(corout), scale_fill_gradient_fun = ggplot2::scale_fill_gradient2(low = "blue", high = "red"))
```

## Other samples
**Note: only 137,316 of the 512,595 peaks in ImmGen were non-zero for these 451 samples**

```{r other, fig.width=7, fig.height=7, message = FALSE, warning = FALSE, echo=FALSE, cache = TRUE}
immgen <- assays(readRDS("../output/immgenDeviations.rds"),"z")[[1]]
zh <- assays(readRDS("../output/other_LPS_Deviations.rds"),"z")[[1]]
zh <- zh[,colSums(is.na(zh)) < 10]
corout <- cor(zh, immgen, use = "pairwise.complete.obs")
heatmaply(t(corout), scale_fill_gradient_fun = ggplot2::scale_fill_gradient2(low = "blue", high = "red"))
```